End-user Web Scraping For Customization

### 2021-02-13 paper.tex
Can now generate pdfs

  In this paper, we extend Wildcard with a new system for \emph{end-user
  web scraping for customization} which enables end-users to create,
  extend and repair adapters by demonstration. We describe three design
  principles that guided our system's development and are applicable to
  other end-user web scraping and customization systems: (a) users
  should be able to scrape data and use it in a single, unified
  environment, (b) users should be able to extend and repair the
  programs that scrape data via demonstration and (c) users should
  receive live feedback during their demonstrations.

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites. We provide example
  usage scenarios that showcase each of our design principles.
\end{abstract}

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Chickenfoot
\citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
and Vegemite {[}lin2009{]} help users tweak and adapt websites to fit
their unique requirements, ranging from reorganizing or annotating
content on the website to automating common tasks. In our prior work, we
presented Wildcard \citep{litt2020a}, a customization system which
enables end-users to customize websites through direct manipulation. It
does this by augmenting websites with a table view that shows their
underlying structured data. The table is bidirectionally synchronized
with the original website, so end-users can easily customize the website
by interacting with the table, including sorting and filtering data,
adding annotations, and running computations in a spreadsheet formula
language.

@@

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, a programming-by-example system for data wrangling,
reported that ``although data scientists were aware of and appreciated
the productivity benefits of existing data wrangling tools, having to
leave their native notebook environment to perform wrangling limited the
usefulness of these tools.'' In web scraping, if a user comes across an
omission while working with data scraped from a website, they need to
switch from the environment in which they are using the data to the
environment in which they wrote their scraping code in order to edit and
re-run it. Sometimes, the divide is more subtle. Vegemite
\citep{lin2009}, a system for end-user programming of mashups, had
separate steps for scraping data from a website and augmenting that data
via automation tasks. During a user study, participants reported that
``it was confusing to use one technique to create the initial table, and
another technique to add information to a new column.''

>>>>

  In this paper, we extend Wildcard with a new system for \emph{end-user
  web scraping for customization} which enables end-users to create,
  extend and repair adapters by demonstration. We describe three design
  principles that guided our system's development and are applicable to
  other end-user web scraping and customization systems: (a) users
  should be able to scrape data and use it in a single, unified
  environment, (b) users should be able to extend and repair the program
  that scrapes data via demonstration and (c) users should receive live
  feedback when providing demonstrations to scrape data.

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites and provide example
  usage scenarios that showcase each of our design principles.
\end{abstract}

@@

Many websites on the internet do not meet the exact needs of all of
their users. End-user web customization systems like Chickenfoot
\citep{bolin2005}, Thresher \citep{hogue2005}, Sifter \citep{huynh2006}
and Vegemite \citep{lin2009} help users tweak and adapt websites to fit
their unique requirements, ranging from reorganizing or annotating
content on the website to automating common tasks. In our prior work, we
presented Wildcard \citep{litt2020a}, a customization system which
enables end-users to customize websites through direct manipulation. It
does this by augmenting websites with a table view that shows their
underlying structured data. The table is bidirectionally synchronized
with the original website, so end-users can easily customize the website
by interacting with the table, including sorting and filtering data,
adding annotations, and running computations in a spreadsheet formula
language.

@@

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, a programming-by-example system for data wrangling,
reported that ``although data scientists were aware of and appreciated
the productivity benefits of existing data wrangling tools, having to
leave their native notebook environment to perform wrangling limited the
usefulness of these tools.'' This was a major reason Wrex was developed
as an add-on to Jupyter notebooks, the environment in which data
scientists use their data. In web scraping, if a user comes across an
omission while working with data scraped from a website, they need to
switch from the environment in which they are using the data to the
environment in which they wrote their scraping code in order to edit and
re-run it. Sometimes, the divide is more subtle. Vegemite
\citep{lin2009}, a system for end-user programming of mashups, had a
unified environment for scraping and augmenting data but separate
interfaces for the scraping and augmentation tasks. During a user study,
participants reported that ``it was confusing to use one technique to
create the initial table, and another technique to add information to a
new column.''
